---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

# 1.Basics R

## Comments
To write a comment, type `#` before the sentence you want to write.
Anything to the right of a `#` in a script will be ignored by R.

## First steps
To understand how R works, you are going to use it as a simple calcuator.
You can get output in the Console simply by typing math in the script and running it:
```{r three-plus-five, echo=TRUE}
3+5 # From the pound sign to the right, this is a comment. I am asking R to sum 3 plus 5
```

Now, try dividing 12 by 2 and write a comment explaining what you are doing
```{r calculator-ex, exercise = TRUE, exercise.lines=5}

```
```{r calculator-ex-solution}
# I am now dividing 12 by 2. The solution is 6
12/6
```

## Assign values to objects
`<-` assigns the values on the right to objects on the left.
```{r print-weight, echo=TRUE}
weight_kg <- 55 # doesn't print anything, but it has created an object called (weight_kg). In Rstudio, you can see it in the Environment window.
```
```{r, echo=TRUE}
(weight_kg <- 55) # Putting parenthesis around the call prints the value of `weight_kg`
```
```{r, echo=TRUE}
weight_kg # and so does typing (or "calling") the name of the object
```
<div id="print-weight-hint">
**Hint:** For a shortcut of `<-`, Type `Alt` + `-` at the same time (for PC), or `Option` + `-` (for Mac).
</div>


We have already created `weight_kg`. Call it.
```{r print-weight-ex, exercise = TRUE, exercise.lines=5}

```
```{r print-weight-ex-solution}
weight_kg
```

R iS cAsE SeNsItIvE!! What happens if you try to call `weight_KG` (note the capitalization in KG)
```{r error-weight-ex, exercise = TRUE, exercise.lines=5}

```

In R, you can overwrite an object, so be careful! For example, run the following line of code and then call `weight_kg`.
```{r print-weight60-ex, exercise = TRUE, exercise.lines=5}
weight_kg <- 60
```
```{r print-weight60-ex-solution}
weight_kg # The value of `weight` is now 60, not 55!
```


## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

